### 2020-06-18 magic_paper.tex
Some small additional things improved. Blended majorization and Wigner functions a bit more. More needed.

\subsection{Majorization in the $\sigma$--fragments}\label{sec:major}

@@

@@

Important examples of resource fragments appear in several established resource theories. \nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.}

@@

\subsection{Mana and Majorization}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds. Mana is the basic resource monotone for magic. Here we show that its basic properties are actually special cases of more general majorization features. More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.

@@

The Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange} is the simplest to analyse, since it only has two distinct components $\{ -\frac{1}{3}, \frac{1}{6} \}$, the latter with a multiplicity of 8.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_k{L_k \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
\end{equation}

>>>>

\subsection{Majorization of quasi-probabilities in the $\sigma$--fragments}\label{sec:major}

@@

\subsection{Lorenz curves for magic states in a $\sigma$--fragment}
With this it is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment. For any $\sigma$ being a full rank free state we have that $W_\sigma(\bmx) $ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.We write $L_{\rho|\sigma}(x)$ for the Lorenz curve of $W_\rho(\bmx)$ with respect to $W_\sigma(\bmx)$.

We now see that $0\le L_{\rho |\sigma}(x) \le 1$ for all $x$ if and only if $\rho$ is a positive Wigner state. Moreover, the area of the function $L_{\rho|\sigma}$ above the line $y=1$ is a resource monotone in this fragment. \ddd{[expand on this -- relate to mana?]}

@@

Important examples of resource fragments appear in several established resource theories. \nick{Need to check if the thermodynamics example works, include magic theories as fragments of $\Rmax$, include Nielsen's bipartite entanglement.} \ddd{[Don't worry about these things now -- let's get the computations section improved]}

@@

\subsection{Magic, Mana and Majorization}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them preceeds. Mana is the basic resource monotone for magic. Here we show that its basic properties are actually special cases of more general majorization features. More precisely its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.

@@

The Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange} is the simplest to analyse, since it only has two distinct components $\{ -\frac{1}{3}, \frac{1}{6} \}$, the latter with a multiplicity of 8.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_k{L_k \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
\end{equation}
\ddd{[We can probably put upper and lower bounds on this value fairly readily. E.g. using known sum rules. Also -- bad choice of variable $k$, using it as index and also copy number. I think $L_{\rho|\sigma}$ is a neater formulation, since you then package things into a single object -- a function.]}
